
# Strawberry
Congyao Duan


## 1.Instrution
   
   First, I use R to clean and select the raw data.I chose strawberry for analysis. 
   Then, I use R to analysis the data. I do some exploratory research to get familiar with this data，but there is no obvious trend. 
   
## 2.Data cleaning

  The data was so jumbled that many columns were mixed together and could not be analyzed， and a lot of variables that are not needed for this project. So do the data cleaning and processing before starting the project.In this part, I separate the mixed columns and remove the unnecessary variables .



```{r setup, include=FALSE, warning=FALSE, message=FALSE}
library(knitr)
library(tidyverse)
library(magrittr)
library(kableExtra)

opts_chunk$set(echo = FALSE, 
               warning = FALSE,
               message = FALSE)
```


```{r}

## read the data

st_data <- read_csv("berries.csv", col_names = TRUE)

## look at number of unique values in each column
st_data %>% summarize_all(n_distinct) -> aa


## make a list of the columns with only one unique value
bb <- which(aa[1,]==1)

## list the 1-unique valu column names 
cn <- colnames(st_data)[bb]

```



```{r}


## remove the 1-unique columns from the dataset
st_data %<>% select(-all_of(bb))

aa %<>% select(-all_of(bb)) 


## State name and the State ANSI code are (sort of) redundant
## Just keep the name
st_data %<>% select(-4)
aa %<>% select(-4) 


kable(head(st_data)) %>% kable_styling(font_size=12)


```



```{r}
berry <- unique(st_data$Commodity)
nberry <- length(berry)

```

This table contains informaton about berries: blueberries, raspberries, and strawberries.
I chose strawberry for analysis. 

### strawberries

```{r}
sberry <- st_data %>% filter((Commodity=="STRAWBERRIES") & (Period=="YEAR"))
sberry %<>% select(-c(Period, Commodity))   

sum(str_detect(sberry$`Data Item`, "^STRAWBERRIES, ")) == length(sberry$`Data Item`)

```

```{r}
#separate the mixed columns“data item"
sberry %<>% separate(`Data Item`, c("B","type", "meas", "what"), sep = ",") 
sberry %<>% select(-B)
```

```{r}
#separate the mixed columns"type"
sberry %<>% separate(type,c("b1", "type", "b2", "lab1", "lab2"), " ")

sberry %<>% select(-c(b1,b2)) 

sberry[is.na(sberry)] <- " "  



```


```{r}


# bberry$Domain %>% unique()

sberry %<>% separate(Domain, c("D_left", "D_right"), sep = ", ")

# bberry$D_left %>% unique()
# bberry$D_right %>% unique()

sberry[is.na(sberry)] <- " "



## bberry$`Domain Category` %>% unique()

sberry %<>% separate(`Domain Category`, c("DC_left", "DC_right"), sep = ", ")


head(sberry$DC_left %>% unique(),n=20)
head(sberry$DC_right %>% unique(), n=20)


sberry %<>% separate(DC_left, c("DC_left_l", "DC_left_r"), sep = ": ")


head(sberry$DC_right %>% unique(), n=20)

sberry %<>% separate(DC_right, c("DC_right_l", "DC_right_r"), sep = ": ") 


sberry[is.na(sberry)] <- " "


```


```{r}

## remove redundant columns

## remove column bberry$DC_left_l


sberry %<>%  select(-DC_left_l) 


sberry %<>% select(-DC_right_l)


sberry %<>% mutate(label = paste(lab1,lab2)) 

## remove "Chemical" and joint the columns

sberry %<>% mutate(D_left = "CHEMICAL", D_left = "") 



sberry %<>% mutate(Chemical=paste(D_left, D_right)) 

sberry %<>% select(-c(D_left, D_right)) 


sberry %<>% select(Year, State, type, what, meas, label, DC_left_r, DC_right_r, Chemical, Value )

```


```{r}
## Merge two columns
## in the column "what"
cnt_1 <- str_detect(sberry$what, "MEASURED IN")
sum(cnt_1)

## in the column "meas"

cnt_2 <- str_detect(sberry$meas, "MEASURED IN")
sum(cnt_2)

##put them all in the same column


f1 <- function(a,b){
  if(a){
    return(b)
  }else{
      return("")
  }
}


index_meas <- str_detect(sberry$meas, "MEASURED IN")

head(index_meas)
new <- map2(index_meas, sberry$meas, f1)
new <- unlist(new)
head(new, n=20)

sberry %<>% mutate(m_in_1 = unlist(map2(index_meas, sberry$meas, f1))) 


sberry %<>% mutate(meas = str_replace(sberry$meas, "MEASURED IN.*$", ""))

cnt_3 <- str_detect(sberry$meas, "MEASURED IN")
sum(cnt_3)

index_what <- str_detect(sberry$what, "MEASURED IN")
sum(index_what)

sberry %<>% mutate(m_in_2 = unlist(map2(index_what, sberry$what, f1))) 

sberry %<>% mutate(what = str_replace(sberry$what, "MEASURED IN.*$", ""))

cnt_what <- str_detect(sberry$what, "MEASURED IN")
sum(cnt_what)

```

```{r}

sberry %<>% mutate(units = str_trim(paste(m_in_1, m_in_2))) 

sberry$units %>% unique()


```

```{r}

## clean it up 

sberry$what %>% unique()  ## rename Avg

sberry$meas %>% unique()  ## rename marketing

sberry$label %>% unique() ## rename harvest 

sberry$DC_left_r %>% unique() # rename chemical_family

tmp <- sberry$DC_right_r %>% unique() # rename materials --213

tmp <- sberry$Value %>% unique() # values

tmp <- sberry$units %>% unique() # Measures




sberry %<>% rename(Avg = what)
sberry %<>% rename(Marketing = meas, Harvest = label, Chem_family = DC_left_r, Materials = DC_right_r, Measures = units)
```


```{r}
colnames(sberry)

sberry %<>% select(Year, State, type, Marketing, 
                   Measures, Avg, Harvest, Chem_family,
                   Materials, Chemical, Value )

str_trim(paste(sberry$Marketing, sberry$Harvest)) %>% unique


sberry %<>% mutate(production = str_trim(paste(Marketing, Harvest)))



sberry %<>% mutate(Chemical = str_trim(paste(Chem_family, Chemical)))

sberry %<>% select(Year, State, type, production, Avg, Measures, Materials, Chemical, Value)

```

##3.Data organization
  After data cleaning,I need to put the data into a format that is easy to analyze. The value part is of character type, which is not convenient for analysis. It needs to be changed into numerical type.

```{r}
ssberry<-subset(sberry,Value!="(NA)"&Value!="(D)")
val<-factor(c(ssberry$Value))
ssberry<-cbind(ssberry,val)
 ssberry$Value<-as.numeric(gsub(",","",ssberry$Value))
```

##4.Exploratory Data Analysis(EDA)
 
   In order to see the distruction of the data clearly,I draw boxplots and violin plots to observe first.Boxplot can not only reflect the distribution characteristics of the original data, but also compare the distribution characteristics of multiple groups of data. It can find the maximum, minimum, median and two quartiles of the data. A boxplot can also be used to find outliers and thus process outliers in data.Violin plots are used to show the distribution and probability density of multiple sets of data. This chart combines the features of box and density charts and is mainly used to show the distribution shape of the data. Similar to the box diagram, but better displayed at the density level.
   
```{r}

a<-unique(ssberry$State)
b<-unique(ssberry$Year)
c<-unique(ssberry$type)
```

```{r}
#Draw boxplots and violin plot
ye1 <- ggplot(ssberry, aes(x=Year, y = Value,group=Year))+ geom_boxplot()+
  labs(x = "Year")
ye1
ye2<-ggplot(data=ssberry,aes(x=Year, y = Value,group=Year))+geom_violin()
ye2
```

```{r}
# excluding outliers
ye3 <- ggplot(ssberry, aes(x=Year, y = Value,group=Year))+ geom_boxplot(outlier.colour = NA) 
ye3

```

```{r}
#Draw boxplots
st1 <- ggplot(ssberry, aes(x=State, y = Value,group=State))+ geom_boxplot()+
  labs(x = "State")
st1
```

```{r}
# excluding outliers
st2 <- ggplot(ssberry, aes(x=State, y = Value,group=State))+ geom_boxplot(outlier.colour = NA) 
st2
```

```{r}
#Draw boxplots
ty1 <- ggplot(ssberry, aes(x=type, y = Value,group=type))+ geom_boxplot()+
  labs(x = "Type")
ty1
```

```{r}
# excluding outliers
ty2 <- ggplot(ssberry, aes(x=type, y = Value,group=type))+ geom_boxplot(outlier.colour = NA) 
ty2
```